PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-04-11 refereeResponse.txt

	Perhaps if we ran some of these simulations for longer, the embryos beyond 60d would all reach \tilde{b} = 2\sqrt{3}. But this requires an intractible number of timesteps, particularly for the fdSteep simulation, where the surface density in the outer disk is quite low. I think the best we can say here is that none of the embryos exceed \tilde{b} = 2\sqrt{3} which is consistent with the oligarchic growth model.
702: Are they that similar? Maybe this statement can be more quantitative? To me it looks like the values fall below 2sqrt(3) at 40 days for fdHiShallow and at 70 days for fdLo. The interpretation that the boundary is only driven by the local value for alpha seems somewhat speculative. I'd also be interested how randomness affects this, i.e. if the simulation is initialized with a different random seed, by how much does the final distribution change?
	We were saving these for the follow up paper, but we do have multiple versions of fdHi, fdSteep and fdShallow! These have now been added to figure 8. The added data does make it clear that the boundary is quite fuzzy. I've also plotted the mean and standard deviation of the \tilde{b} in a number of orbital period bins. I think this makes the accretion boundary a little more apparent. With the exception of maybe the fdShallow simulation, the locations in the disk where \tilde{b} drops below 2\sqrt{3} are broadly consistent, which supports our claim that the boundary location is driven by the local value of alpha.
	TODO: Update text to recflect changes to figure.

5.5. Assembly History of Embryos
719: add references.
	Done
721: Does this distinction have analogies in galaxy formation? Also isn't this overly strict? I would expect that the initial population has quickly collided at least once, so most of the collisions will be major mergers under this definition. This seems to be supported by Fig. 9 where the smooth accretion fraction is always <10%.
	TODO: Ask tom about this?
724: Why are only the 100 largest bodies chosen? It seems more natural to me to choose a mass cut-off. Also, given that in Fig9 is plotting mass on a log-scale, I suggest just plotting the entire population including those planetesimals that remained relatively small and pristine. Also, why is the fdHi simulation chosen?
	TODO: What else to include here? Everything?
726: I think it could be explicitly stated that smooth accretion = minor mergers.
730 & onwards: Can the authors quantify this trend? E.g., by making three linear fits (with error bars) for > 60d, < 60d and the full population. I'm in particular unconvinced that the trend for P > 60 days truly is flat, given the small sample size for larger bodies.
Figure 9:
Given that I'm skeptical about the 60 day boundary being clear and universal, I think this plot would be stronger if the bodies were colored by orbital period (in addition to the marker style indicating this boundary), and the plot would include a corresponding colorbar.
The authors state "there is a decreasing correlation between smooth accretion fraction and mass, which suggests that most growth occurs between equal mass bodies". As far as I understand, this doesn't have to be the case. I would argue that more massive bodies require more time to build up and during later stages there are simply less primordial planetesimals left so collisions are just more likely to be major mergers.
The authors state "indicating that accretion of planetesimals is important during all phases of the evolution", yet the smooth accreting fraction is only between 1-10% for all these bodies. Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
	I agree that 1-10% is a small fraction. The mass cutoff should definitely be larger. TODO: Change mass cutoff and hopefully the same scaling with mass remains.
In the legend, I think "orbit" should be put in the subscript instead of P_orbit
746: This is just because in the inner disk there are no primordial planetesimals left to build the more massive bodies, right?
	No, the accretion mode should be qualitatively different, even before the planetesimals run out. TODO: Hopefully including more data in the plot and maybe increasing the mass cutoff for 'smooth' accretion will make this more obvious.
750: use /citep[see][]{Kokubo}
	Fixed
756: I agree that the large bodies must've originated due to mergers with other embryos, but this is not really an explanation for why the feeding zone size doesn't match the theoretical value, no? Instead it's the lack of gravitational scattering, as the authors write above. Maybe the authors can clarify specifically why oligarchic growth models predict this feeding zone size, and also why gravitational scattering is suppressed in the inner disk (due to the lack of primordial planetesimals in the inner disk?).
766: "One should note that [...]." This sentence can be deleted in my opinion.
	Removed
Figure 10:
I suggest indicating the boundary between accretion modes in this figure. >60d orbits only include 4-5 bodies. However, to me it seems like the shape of the accretion zone is qualitatively the same until ~ 20 orbits, which strengthens my view that the 60d orbit boundary is not very clear at all.
I suggest matching the x-axis limits the shown xdata.
I think "Fraction of planetesimals accreted" is a somewhat misleading description of what the plot is showing. What about: "Distribution of accreted planetesimals"?
775: The transition between smooth and unimodal seems to be happening at about 20 days to me.
Figure 11
The y-axis label overlap
I think the finding that the crossing of alpha = 0.1 in the bottom panel well matches the crossing of tilde b = 2 sqrt(3) is interesting and worth highlighting more, maybe with some vertical lines? Is there a meaning behind alpha = 0.1, i.e., is this coming from some analytical consideration? See my major comments

### 2023-04-11 main.tex
Edits up to fig 10

We begin by investigating the ``smoothness'' of the accretion events
that give rise to each embryo. Drawing from a common technique used
for cosmological simulations of galaxy formation, we divide growth events for
a given body into ``major'' and ``minor'' mergers. Here, we define minor events as any collision involving an initial mass 
planetesimal, while major events consist of a merger between any two larger bodies. In figure \ref{fig:minor_frac}, we choose the 
100 largest bodies at the end of the fdHi simulation, retrieve all collision events involving these bodies, and plot the total mass 
fraction attained through minor events as a function of the final mass of the body. The bodies are then subdivided into those that 
end up with orbital periods greater than 60 days (red x's) and less than 60 days (blue dots). For the bodies in the outer oligarchic 
growth region, the trend between smooth accretion mass fraction and final mass is nearly flat. Regardless of how much an 
embryo has grown, mergers with initial mass planetesimals contribute on the order of a few percent to the final mass.
At shorter orbital periods, however, the contribution from minor mergers can be over an order of magnitude smaller as the 
embryos mature.

@@

The variation in smooth accretion fraction with mass for the short period bodies suggests that the planetesimal and embryo populations interact differently than those in the outer disk. Exterior to the 60 day accretion mode boundary, the growing embryos continue to accrete planetesimals as they near their final mass. Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role. Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion (see \citet{kokubo98}), and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits. As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model. Figure \ref{fig:minor_frac} suggests that the extra mass here obtain comes from mergers with the other nearby embryos.

Another line of evidence pointing to a lack of gravitational
scattering and orbital repulsion in the inner disk can be seen in
figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive
bodies from the fdHi simulation and arranged them in order of final
orbital period. On each line, the blue
hash mark indicates the present orbital period of an embryo and the histogram represents the initial orbital period distribution of the planetesimals used to construct the embryo. One should note that unlike the previous figure, this plot shows where every single bit of mass (in the form of planetesimals) originated, rather than only indicating the result of direct collisions with the embryos.

>>>>

We begin by investigating the ``smoothness'' of the accretion events
that give rise to each embryo. Drawing from a common technique used
for cosmological simulations of galaxy formation, we divide growth events for
a given body into ``major'' and ``minor'' mergers \citep{kauffmann93, murali02, lhullier12}. 
Here, we define minor events as any collision involving an initial mass 
planetesimal, while major events consist of a merger between any two larger bodies. In figure \ref{fig:minor_frac}, we choose the 
100 largest bodies at the end of the fdHi simulation, retrieve all collision events involving these bodies, and plot the total mass 
fraction attained through minor events as a function of the final mass of the body. The bodies are then subdivided into those that 
end up with orbital periods greater than 60 days (red x's) and less than 60 days (blue dots). For the bodies in the outer oligarchic 
growth region, the trend between smooth accretion mass fraction and final mass is nearly flat. Regardless of how much an 
embryo has grown, mergers with initial mass planetesimals contribute on the order of a few percent to the final mass.
At shorter orbital periods, however, the contribution from minor mergers can be over an order of magnitude smaller as the 
embryos mature.

@@

The variation in smooth accretion fraction with mass for the short period bodies suggests that the planetesimal and embryo populations interact differently than those in the outer disk. Exterior to the 60 day accretion mode boundary, the growing embryos continue to accrete planetesimals as they near their final mass. Inside the boundary, however, later growth events tend to be dominated by embryo-embryo collisions, and the smooth accretion fraction drops as mergers with planetesimals play a less significant role. Gravitational scattering between embryos and planetesimals is a key ingredient for orbital repulsion \citep{kokubo98}, and so a lack of gravitational scattering in the inner disk should prevent the embryos from settling onto neatly-spaced, isolated orbits. As we showed in figure \ref{fig:surfden_b}, the embryos in the inner disk appear to reach well beyond the typical feeding zone size predicted by an oligarchic growth model. Figure \ref{fig:minor_frac} suggests that the extra mass here obtain comes from mergers with the other nearby embryos.

Another line of evidence pointing to a lack of gravitational
scattering and orbital repulsion in the inner disk can be seen in
figure \ref{fig:acc_zones}. Here, we have chosen the 20 most massive
bodies from the fdHi simulation and arranged them in order of final
orbital period. On each line, the blue
hash mark indicates the present orbital period of an embryo and the histogram represents the initial orbital period distribution of the planetesimals used to construct the embryo.
